### 2015-05-08 papers/histogram/thesis/thesis.tex
removing wang landau from thesis for now

To find $\bk{X}_T$, we first need to understand the concept of a
density of states. Given an arbitrary system property $Y\p{s}$
(e.g. energy) determined by the microstate $s$, one can define a
density of states $D\p{Y}$ such that
\begin{enumerate*}[label=\roman*)]
\item for arbitrary $Y_0$, the value of $D\p{Y_0}$ is proportional to
  the number of microstates $s$ for which $Y\p{s}=Y_0$, and
\item $\sum_YD\p{Y}=1$.
\end{enumerate*}
The units of $D\p{Y}$ are inverse to the units of $Y$. The temperature
dependence of $\bk{X}_T$ can be expressed in terms of the expectation
value $\bk{X}_E$ and the density of states $D\p{E}$ by
\begin{align}
  \bk{X}_T=\f1{Z\p{T}}\sum_E\bk{X}_ED\p{E}e^{-E/kT},
  \label{eq:XT_norm}
\end{align}
where the partition function $Z\p{T}$ is simply a normalization
factor, given by
\begin{align}
  Z\p{T}=\sum_ED\p{E}e^{-E/kT}.
\end{align}
To reduce redundant computations and numerical error in
implementation, we will generally use a partition function with an
unnormalized density of states $\tilde D\p{E}$, i.e.
\begin{align}
  \tilde Z\p{T}=\sum_E\tilde D\p{E}e^{-E/kT},
\end{align}
in terms of which
\begin{align}
  \bk{X}_T=\f1{\tilde Z\p{T}}\sum_E\bk{X}_E\tilde D\p{E}e^{-E/kT}.
  \label{eq:XT}
\end{align}

@@

The partition function at $T=T_0$ for simulations with canonical
weights is
\begin{align}
  \tilde Z\p{T_0}=\sum_E\tilde D\p{E}e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{w\p{E}}~e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{e^{-E/kT_0}}~e^{-E/kT_0}=\sum_EH\p{E},
  \label{Z_canonical}
\end{align}
and the value of a thermodynamic property $X\p{T_0}$
\begin{align}
  X\p{T_0}=\f1{\tilde Z\p{T_0}}\sum_E\bk{X}_E\tilde D\p{E}e^{-E/kT_0}
  =\f{\sum_E\bk{X}_EH\p{E}}{\sum_EH\p{E}},
  \label{eq:X_canonical}
\end{align}
where $\bk{X}_E$ is the mean value of $X$ at the energy $E$. The
simplifications in in (\ref{Z_canonical}) and (\ref{eq:X_canonical}),
which have no explicit dependence on $T_0$, occur because canonical
Monte Carlo simulations sample energies in proportion to the
distribution (over energy) of microstates at a temperature of $T_0$.
Canonical Monte Carlo simulations can therefore fail to sufficiently
sample energies which are important (i.e. energies with a
non-negligible state probability density) at different
temperatures. As a consequence, such simulations should not be used to
determine properties $X\p{T\ne T_0}$, and are thus referred to as
``fixed temperature'' simulations. Incidentally, Metropolis Monte
Carlo simulations can be thought of as infinite-temperature
simulations, as they are equivalent to simulations with canonical
weights
\begin{align}
  w\p{E}=\lim_{T\to\infty}e^{-E/kT}=1.
  \label{eq:inf_temp_weights}
\end{align}
This observation will be used in Section \ref{sec:min_energy} to
identify a maximum energy of interest.

@@

The first of these parameters, $n$, controls how often to check the
flatness condition $C\sp{H}$ and run updates, if necessary. The value
of $n$ is not too important, so long as it is reasonable for the
system at hand. Too small value of $n$ will waste computation time
determining $C\sp{H}$, while too large of a value will waste time
simulating when $C\sp{H}$ has already been satisfied. In general, $n$
should be proportional to the computation time of $C\sp{H}$, which
scales with energy range of the simulated system. We therefore use
$n=L$, where $L$ is, as described in Section \ref{sec:simple_flat},
the number of energy levels for the given square-well fluid. Other
works typically neglect providing any heuristic or formula for $n$,
reporting a system-independent $n=10^3$\cite{wang_landau_mod} or
$10^5$\cite{wang_landau}.  \fixme{find more citations for this last
  claim}

The next parameter, $f_0$, controls the initial amount by which to
adjust the weight of the current energy after each move. As mentioned
in Algorithm \ref{alg:wang_landau}, one should always have $f_0>1$,
but the appropriate value of $f_0$ will generally depend on the system
at hand. Too large a value of $f_0$ will magnify stochastic error in
initialization, while too small a value of $f_0$ will cause
simulations to take an exceedingly long time to converge. Lacking any
heuristics for assigning $f_0$, literature typically suggests $f_0=e$
\cite{wang_landau}. After some experimentation with the free
parameters in the Wang-Landau method, we decided on $f_0=e^{1/8}$. In
practice, one usually works with $\ln f$, making the commonly
suggested value $\ln f_0=1$ and our own $\ln f_0=1/8$.

The factor $u$ appearing in step \ref{alg:wang_landau_update} of
Algorithm \ref{alg:wang_landau} controls the amount by which to adjust
$f$ when the histogram $H\p{E}$ is sufficiently flat. In principle,
one need not take a root of $f$ at each reset: the general idea behind
Algorithm \ref{alg:wang_landau} requires only $f_k<f_{k-1}$ to
converge (assuming that $C\sp{H}$ can be satisfied) and
$\lim_{k\to\infty}f_k=1$ to terminate. Taking the $u$-th root of $f$
at each increment of $k$ is a natural and convenient iterative means
to satisfy these requirements. Previous works have reported using
values such as $u=2$ \cite{wang_landau, wang_landau_mod} and $u=10$
\cite{wang_landau_analysis}; we use the former, conservatively
favoring more initialization iterations by decreasing $f$ by a smaller
amount on each reset.

@@

The success of Wang-Landau thus relies on some degree of leniency in
the flatness condition, which makes tuning $C\sp{H}$ crucial to the
efficient and effective implementation of this method. Some previous
works\cite{wang_landau} suggest that $C\sp{H}$ should be made as
stringent as possible, cautioning only that some simulations might not
satisfy too strict of a flatness condition in any reasonable amount of
time. These works fail to recognize the reliance of Wang-Landau on the
{\it failure} of $C\sp{H}$ to enforce a perfectly flat histogram. A
commonly suggested flatness condition is that the minimum histogram
value in some specified range of energies be at least some fixed
proportion of the mean histogram value, i.e.
$C\sp{H}:\min\sp{H\p{E}}\ge x\bk{H}_E$, and several papers report
using $x=0.95$. We used the same condition with $x=0.25$. Determining
the range of energies over which to evaluate $C\sp{H}$ is the subject
of Section \ref{sec:min_energy}.

@@

Once we identify an energy $E_-$ satisfying (\ref{eq:min_E_condition})
in an initialization routine for any histogram method, we effectively
forbid transitions to energies $E<E_-$ by tentatively setting weights
$w\p{E<E_-}=e^{-\p{E-E_-}/kT}$ for some temperature $T\ll
T_{\t{min}}$. These weights prevent the initialization routine from
wasting time on energies at which we will override the weight array
after initialization anyways. A special case was made for Wang-Landau,
as the design of this method assumes knowledge of the energy range of
interest a priori. In order to fairly compare Wang-Landau to other
methods, we therefore identified $E_-$ for each simulated system using
other methods, and hard-coded the minimum important energies for each
system into the Wang-Landau initialization routines. \fixme{talk about
  how bad this is} We always set
$w\p{E<E_-}=e^{-\p{E-E_-}/kT_{\t{min}}}$ after initialization of all
histogram methods with $kT_{\t{min}}=0.2\epsilon$. We chose this
temperature because it is right below the temperature at which the
square-well fluid condenses from a gas into a liquid (see Section
\ref{sec:properties}). \fixme{what about pressure?}

@@

Having developed and implemented all of the histogram methods
discussed in Section \ref{sec:methods}, we will now look at the
results from simulating with these methods. Due to time constraints,
we simulated only one system: the well width $\lambda=1.3$ and filling
fraction $\eta=0.3$ square-well fluid, for all sizes (i.e. number of
spheres) $N\in\sp{5,25}$. We initialized histogram methods for
$10^5N^2$ iterations ($10^5N^3$ moves), and simulated for just as long
afterwards. To check for consistency in simulation results, we
simulated each combination of histogram method and system size for 30
different random number generator seeds.

@@

Three arrays contain the raw data for all analysis performed in this
paper:

\fixme{Give examples of energy histograms for one system, density of
  states for several $N$, and perhaps a weight array.}

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{figs/array-example.pdf}
  \caption[Example arrays]
  {Example arrays computed by various histogram methods for a
    square-well fluid with a well width $\lambda=1.3$, filling
    fraction $\eta=0.3$, and $N=25$ spheres after simulating for
    $10^5N^2$ iterations: (top left) energy histogram, (top right)
    weight array, (bottom left) density of states.}
  \label{fig:arrays}
\end{figure}

\subsection{Sample rates}
\label{sec:sample_rates}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.8\textwidth]{figs/sample-rate-example.pdf}
  \caption[Example energy sampling rates]
  {Example pessimistic energy sampling rates computed by various
    histogram methods for a square-well fluid with a well width
    $\lambda=1.3$, filling fraction $\eta=0.3$, and $N=25$ spheres
    after simulating for $10^5N^2$ iterations. Sample rates for each
    method are averaged over 30 simulations with different random
    number seeds.}
  \label{fig:sample_rates}
\end{figure}

@@

\fixme{Discuss errors in computed thermodynamic properties. Introduce
  converged flat weights.}

\subsubsection{Example curves}
\label{sec:property_examples}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.7\textwidth]{figs/internal-energy.pdf}
  \caption[Internal energy]
  {Specific internal energy}
  \label{fig:internal_energy}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/heat-capacity.pdf}
  \caption[Heat capacity]
  {Specific heat capacity}
  \label{fig:heat_capacity}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/config-entropy.pdf}
  \caption[Configurational entropy]
  {Specific configurational entropy}
  \label{fig:config_entropy}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]
  {figs/internal-energy-err.pdf}
  \caption[Errors in internal energy]
  {Errors in specific internal energy}
  \label{fig:internal_energy_err}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/heat-capacity-err.pdf}
  \caption[Errors in heat capacity]
  {Errors in specific heat capacity}
  \label{fig:heat_capacity_err}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/config-entropy-err.pdf}
  \caption[Errors in configurational entropy]
  {Errors in specific configurational entropy}
  \label{fig:config_entropy_err}
\end{figure}

\subsubsection{Error scaling and comparisons}
\label{sec:errors}

\begin{figure}[H]
  \centering
    \includegraphics[width=0.7\textwidth]{figs/u-scaling.pdf}
  \caption[Internal energy error scaling]
  {Specific internal energy error scaling}
  \label{fig:u_scaling}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/cv-scaling.pdf}
  \caption[Heat capacity error scaling]
  {Specific heat capacity error scaling}
  \label{fig:cv_scaling}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/s-scaling.pdf}
  \caption[Configurational entropy error scaling]
  {Specific configurational entropy error scaling}
  \label{fig:s_scaling}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]
  {figs/internal-energy-comps.pdf}
  \caption[Internal energy error comparisons]
  {Internal energy error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/heat-capacity-comps.pdf}
  \caption[Heat capacity error comparisons]
  {Heat capacity error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/config-entropy-comps.pdf}
  \caption[Configurational entropy error comparisons]
  {Configurational entropy error comparisons}
  \label{fig:u_comps}
\end{figure}

>>>>

To find $\bk{X}_T$, we first need to understand the concept of a
density of states. Given an arbitrary system property $Y\p{s}$
(e.g. energy) determined by the microstate $s$, one can define a
density of states $D\p{Y}$ such that
\begin{enumerate*}[label=\roman*)]
\item for arbitrary $Y_0$, the value of $D\p{Y_0}$ is proportional to
  the number of microstates $s$ for which $Y\p{s}=Y_0$, and
\item $\sum_YD\p{Y}=1$.
\end{enumerate*}
The units of $D\p{Y}$ are inverse to the units of $Y$. The temperature
dependence of $\bk{X}_T$ can be expressed in terms of the expectation
value $\bk{X}_E$ and the density of states $D\p{E}$ by
\begin{align}
  \bk{X}_T=\f1{Z\p{T}}\sum_E\bk{X}_ED\p{E}e^{-E/kT},
  \label{eq:XT_norm}
\end{align}
where the partition function $Z\p{T}$ is simply a normalization
factor, given by
\begin{align}
  Z\p{T}=\sum_ED\p{E}e^{-E/kT}.
  \label{eq:Z_norm}
\end{align}
To reduce redundant computations and numerical error in
implementation, we will generally use a partition function with an
unnormalized density of states $\tilde D\p{E}$, i.e.
\begin{align}
  \tilde Z\p{T}=\sum_E\tilde D\p{E}e^{-E/kT},
  \label{eq:Z}
\end{align}
in terms of which
\begin{align}
  \bk{X}_T=\f1{\tilde Z\p{T}}\sum_E\bk{X}_E\tilde D\p{E}e^{-E/kT}.
  \label{eq:XT}
\end{align}

@@

The partition function at $T=T_0$ for simulations with canonical
weights is
\begin{align}
  \tilde Z\p{T_0}=\sum_E\tilde D\p{E}e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{w\p{E}}~e^{-E/kT_0}
  =\sum_E\f{H\p{E}}{e^{-E/kT_0}}~e^{-E/kT_0}=\sum_EH\p{E},
  \label{Z_canonical}
\end{align}
and the value of a thermodynamic property $\bk{X}_{T_0}$
\begin{align}
  \bk{X}_{T_0}=\f1{\tilde Z\p{T_0}}\sum_E\bk{X}_E\tilde
  D\p{E}e^{-E/kT_0} =\f{\sum_E\bk{X}_EH\p{E}}{\sum_EH\p{E}},
  \label{eq:X_canonical}
\end{align}
where $\bk{X}_E$ is the mean value of $X$ at the energy $E$. The
simplifications in in (\ref{Z_canonical}) and (\ref{eq:X_canonical}),
which have no explicit dependence on $T_0$, occur because canonical
Monte Carlo simulations sample energies in proportion to the
distribution (over energy) of microstates at a temperature of $T_0$.
Canonical Monte Carlo simulations can therefore fail to sufficiently
sample energies which are important (i.e. energies with a
non-negligible state probability density) at different
temperatures. As a consequence, such simulations should not be used to
determine properties $\bk{X}_{T\ne T_0}$, and are thus referred to as
``fixed temperature'' simulations. Incidentally, Metropolis Monte
Carlo simulations can be thought of as infinite-temperature
simulations, as they are equivalent to simulations with canonical
weights
\begin{align}
  w\p{E}=\lim_{T\to\infty}e^{-E/kT}=1.
  \label{eq:inf_temp_weights}
\end{align}
This observation will be used in Section \ref{sec:min_energy} to
identify a maximum energy of interest.

@@

The first of these parameters, $n$, controls how often to check the
flatness condition $C\sp{H}$ and run updates, if necessary. The value
of $n$ is not too important, so long as it is reasonable for the
system at hand. Too small value of $n$ will waste computation time
determining $C\sp{H}$, while too large of a value will waste time
simulating when $C\sp{H}$ has already been satisfied. In general, $n$
should be proportional to the computation time of $C\sp{H}$, which
scales with energy range of the simulated system. We therefore use
$n=L$, where $L$ is, as described in Section \ref{sec:simple_flat},
the number of energy levels for the given square-well fluid. Other
works typically neglect providing any heuristic or formula for $n$,
reporting a system-independent $n=10^3$\cite{wang_landau_mod} or
$10^5$\cite{wang_landau}.

The next parameter, $f_0$, controls the initial amount by which to
adjust the weight of the current energy after each move. As mentioned
in Algorithm \ref{alg:wang_landau}, one should always have $f_0>1$,
but the appropriate value of $f_0$ will generally depend on the system
at hand. Too large a value of $f_0$ will magnify stochastic error in
initialization, while too small a value of $f_0$ will cause
simulations to take an exceedingly long time to converge. Lacking any
heuristics for assigning $f_0$, we use $f_0=e$ (more precisely, $\ln
f_0=1$), a value commonly suggested by literature\cite{wang_landau}.

The factor $u$ appearing in step \ref{alg:wang_landau_update} of
Algorithm \ref{alg:wang_landau} controls the amount by which to adjust
$f$ when the histogram $H\p{E}$ is sufficiently flat. In principle,
one need not take a root of $f$ at each reset: the general idea behind
Algorithm \ref{alg:wang_landau} requires only $f_k<f_{k-1}$ to
converge (assuming that $C\sp{H}$ can be satisfied) and
$\lim_{k\to\infty}f_k=1$ to terminate. Taking the $u$-th root of $f$
at each increment of $k$ is a natural and convenient iterative means
to satisfy these requirements. Previous works have reported using
values such as $u=2$ \cite{wang_landau, wang_landau_mod} and $u=10$
\cite{wang_landau_analysis}; we use the former value.

@@

The success of Wang-Landau thus relies on some degree of leniency in
the flatness condition, which makes tuning $C\sp{H}$ crucial to the
efficient and effective implementation of this method. Some previous
works\cite{wang_landau} suggest that $C\sp{H}$ should be made as
stringent as possible, cautioning only that some simulations might not
satisfy too strict of a flatness condition in any reasonable amount of
time. These works fail to recognize the reliance of Wang-Landau on the
{\it failure} of $C\sp{H}$ to enforce a perfectly flat histogram. A
commonly suggested flatness condition is that the minimum histogram
value in some specified range of energies be at least some fixed
proportion of the mean histogram value, i.e.
$C\sp{H}:\min\sp{H\p{E}}\ge x\bk{H}_E$, and several papers report
using $x=0.95$. We use this condition with the same value of
$x$. Determining the range of energies over which to evaluate
$C\sp{H}$ is the subject of Section \ref{sec:min_energy}.

@@

Once we identify an energy $E_-$ satisfying (\ref{eq:min_E_condition})
in an initialization routine for any histogram method, we effectively
forbid transitions to energies $E<E_-$ by tentatively setting weights
$w\p{E<E_-}=e^{-\p{E-E_-}/kT}$ for some temperature $T\ll
T_{\t{min}}$. These weights prevent the initialization routine from
wasting time on energies at which we will override the weight array
after initialization anyways. A special case was made for Wang-Landau,
as the design of this method assumes knowledge of the energy range of
interest a priori. In order to fairly compare Wang-Landau to other
methods, we therefore identified $E_-$ for each simulated system using
other methods, and hard-coded the minimum important energies for each
system into the Wang-Landau initialization routines\fixme{talk about
  how bad this is}. We always set
$w\p{E<E_-}=e^{-\p{E-E_-}/kT_{\t{min}}}$ after initialization of all
histogram methods with $kT_{\t{min}}=0.2\epsilon$. We chose this
temperature because it is right below the temperature at which the
square-well fluid condenses from a gas into a liquid (see Section
\ref{sec:errors}). \fixme{what about pressure?}

@@

Having developed and implemented all of the histogram methods
discussed in Section \ref{sec:methods}, we will now look at the
results from simulating with these methods. Due to time constraints,
we simulated only one system, the square-well fluid with well width
$\lambda=1.3$ and filling fraction $\eta=0.3$, for sizes (i.e. number
of spheres) $N\in\sp{5,25}$. We initialized histogram methods for
$10^5N^2$ iterations ($10^5N^3$ moves), and simulated for just as long
afterwards. To check for consistency in simulation results, we
simulated each combination of histogram method and system size for 30
different random number generator seeds.

\subsection{Controls}
\label{sec:controls}

Our analysis will involve comparing errors in system properties
computed from simulation results. As we do not know the true values of
these system properties, we will compare standard simulation results
against those from ``gold standard'' simulations, which run for
significantly longer than the standard $10^5N^2$ iterations. For our
gold standard simulations, we use the TMMC method and initialize until
it collects $10^4$ optimistic samples of the minimum important energy
(i.e. until $s_o\p{E_-}\ge 10^4$). To increase confidence in
low-temperature gold standard results, we initialized them with
$kT_{\t{min}}=0.1\epsilon$. After initialization, the gold standard
runs simulate for $10^{10}$ iterations ($10^{10}N$ moves). While the
entire initialization and simulation process takes around two hours
for the largest regular simulations, the largest golden simulations
initialize for $\sim11$ hours, and simulate for a week. To control for
iteration number in the quality of results, we compare against a
``converged flat'' simulation. Converged flat simulations use the
golden (flat histogram) weight array, but simulates for the same
number of iterations as the standard simulations.

@@

\begin{figure}[!b]
  \centering
  \includegraphics[width=\textwidth]{figs/array-example.pdf}
  \caption[Example arrays]
  {Example arrays computed by various histogram methods for a
    square-well fluid with a well width $\lambda=1.3$, filling
    fraction $\eta=0.3$, and $N=25$ spheres after simulating for
    $10^5N^2$ iterations: (top left) energy histogram, (top right)
    weight array, (bottom left) density of states. Vertical reference
    lines denote the minimum important energy $E_-$.}
  \label{fig:arrays}
\end{figure}

Most of our analysis will use quantities computed from two arrays
given by simulations: the energy histogram $H\p{E}$ and the weights
$w\p{E}$. To get a sense of what these arrays look like, Figure
\ref{fig:arrays} shows the energy histogram and weights from an $N=25$
simulation, along with the density of states computed via $\tilde
D=H/w$ and normalized to have a maximum value of 1. The vertical
reference line in these plots denotes the minimum important energy
$E_-$. These plots demonstrate that, as expected, different methods
can accumulate different histograms $H$ and weights $w$, yet agree on
system properties such as the density of states $D$.

Though high energy histogram counts at low energies mean that a
simulation has collected many statistics on these energies, the energy
histogram says nothing about how correlated different energy
observations are. To determine how effective different simulations are
at collecting uncorrelated statistics, we can look at the pessimistic
sample rate $r_p\p{E}$, which is the mean number of simulation
iterations required to sample a given energy $E$. This rate is given
in terms of the number of iterations $I$ in a simulation (where we
always have $I=10^5N^2$) and the pessimistic sample rate $s_p\p{E}$ by
$r_p\p{E}=I/s_p\p{E}$. Figure \ref{fig:sample_rates} shows pessimistic
sample rates for all methods averaged over 30 random number seeds for
$N=25$ simulations. Lower pessimistic sample rates mean that a
simulation takes less time to collect statistics which are guaranteed
to be uncorrelated.

\fixme{talk about plots}

\begin{figure}[!b]
  \centering
  \includegraphics[width=0.8\textwidth]{figs/sample-rates.pdf}
  \caption[Example energy sampling rates]
  {Example pessimistic energy sampling rates computed by various
    histogram methods. Sample rates for each method are averaged over
    30 simulations with different random number seeds. The vertical
    reference line denotes the minimum important energy $E_-$.}
  \label{fig:sample_rates}
\end{figure}

@@

We can use the formula in (\ref{eq:XT}) to compute the temperature
dependence of a few system properties directly from the density of
states, such as the internal energy
\begin{align}
  U=\bk{E}_T,
  \label{eq:U}
\end{align}
the heat capacity
\begin{align}
  C_V\p{T}=\f{\partial U}{\partial T}
  =\bk{\p{\f{E}{kT}}^2}_T-\bk{\f{E}{kT}}_T^2,
  \label{eq:CV}
\end{align}
and the configurational entropy\fixme{how is this different from
  regular entropy?}
\begin{align}
  S_{\t{config}}\p{T}=k\bk{\f{E}{kT}+\ln Z}_T.
  \label{eq:S}
\end{align}
Figures \ref{fig:internal_energy}--\ref{fig:config_entropy} show these
properties as computed via all methods for a single $N=25$ simulation
each. When looking at these figures, one should remember that results
are only trusted down to $kT=0.2\epsilon$ for regular simulations, and
$kT=0.1\epsilon$ for golden ones. As with the density of states, all
histogram methods agree fairly well on the physical properties of the
square-well fluid. Though Figures
\ref{fig:internal_energy}--\ref{fig:config_entropy} are interesting
for studying the square-well fluid, they do not help us resolve the
efficacy of different histogram methods. These figures do, however,
show that the square-well fluid has a phase transition around
$kT\approx0.5\epsilon$, which justifies our choice of
$kT_{\t{min}}=0.2\epsilon$ and ensures that the histogram methods are
performing the nontrivial task of exploring the liquid-gas
phase boundary of the square-well fluid. For the purposes of this
paper, we will neglect to demonstrate that this phase transition is
indeed between liquid and gas, and take this fact as given.

Having a sense of how $U$, $C_V$ and $S_{\t{config}}$ depend on
temperature, we can now look at the how the errors $\Delta U$, $\Delta
C_V$ and $\Delta S_{\t{config}}$ relative to the TMMC golden
calculations. These are shown for a single $N=25$ simulation in
Figures \ref{fig:internal_energy_err}--\ref{fig:config_entropy_err}.

\begin{figure}[b]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/internal-energy.pdf}
  \caption[Internal energy]
  {Specific internal energy curves from single $N=25$ simulations.}
  \label{fig:internal_energy}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figs/heat-capacity.pdf}
  \caption[Heat capacity]
  {Specific heat capacity curves from single $N=25$ simulations.}
  \label{fig:heat_capacity}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/config-entropy.pdf}
  \caption[Configurational entropy]
  {Specific configurational entropy curves from single $N=25$
    simulations.}
  \label{fig:config_entropy}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]
  {figs/internal-energy-err.pdf}
  \caption[Internal energy error scaling]
  {Errors in specific internal energy from single $N=25$ simulations.}
  \label{fig:internal_energy_err}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/heat-capacity-err.pdf}
  \caption[Heat capacity error scaling]
  {Errors in specific heat capacity from single $N=25$ simulations.}
  \label{fig:heat_capacity_err}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/config-entropy-err.pdf}
  \caption[Configurational entropy error scaling]
  {Errors in specific configurational entropy from single $N=25$
    simulations.}
  \label{fig:config_entropy_err}
\end{figure}

\subsubsection{Error scaling}
\label{sec:scaling}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/u-scaling.pdf}
  \caption[Internal energy error scaling]
  {Errors in internal energy as computed by various histogram methods,
    each averaged over 30 simulations with different random number
    seeds.}
  \label{fig:u_scaling}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figs/cv-scaling.pdf}
  \caption[Heat capacity error scaling]
  {Errors in specific heat capacity as computed by various histogram
    methods, each averaged over 30 simulations with different random
    number seeds.}
  \label{fig:cv_scaling}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figs/s-scaling.pdf}
  \caption[Configurational entropy error scaling]
  {Errors in specific configurational entropy as computed by various
    histogram methods, each averaged over 30 simulations with
    different random number seeds.}
  \label{fig:s_scaling}
\end{figure}

\subsubsection{Error comparisons}
\label{sec:errors}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]
  {figs/internal-energy-comps.pdf}
  \caption[Internal energy error comparisons]
  {Internal energy error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figs/heat-capacity-comps.pdf}
  \caption[Heat capacity error comparisons]
  {Heat capacity error comparisons}
  \label{fig:u_comps}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.75\textwidth]{figs/config-entropy-comps.pdf}
  \caption[Configurational entropy error comparisons]
  {Configurational entropy error comparisons}
  \label{fig:u_comps}
\end{figure}
